### 2016-05-20 intro.tex
cheers

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k). However, Squid employs a very efficient method using a fixed number - four. Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks. Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e. an index into the bit array.  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above. This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}

>>>>

\section{Introduction}
\paragraph{Basic issues in Naor-Yogev. }
\begin{itemize}
\item The NY paper formalizes and investigates a security notion of limited interest
\item The proposed construction won't scale in common network applications
\item The main results are of theoretical interest only
\item The basic syntax and operation of their Bloom filter formalization is underdefined.  (This really irritates me.)  It isn’t clear that their Bloom filter formalization actually captures traditional Bloom filters! \tsnote{UPDATE (5/20/16): It is clear, now, that it \emph{does not}.}
\item The ``adversarial-resilient Bloom Filter'' definition does not give the adversary access to the hash functions that created the representation; effectively, they are secret.  This strikes me as quite odd, and seems to miss the point that finding a false positive should be hard, in practice, even if you know that the hash functions are $h_i(X)=\mathrm{SHA256}(\langle i \rangle \concat X)$.  (If the hash functions are not kept secret, the whole [NY] security notion kind of unravels; the adversary already is given~$S$, so if it knows the hash functions then you might as well just give it the whole Bloom filter data structure.) \tsnote{In the Squid proxy, the hash functions are not secret: you can download the source code, and the docs (available online even!) tell you that ``The protocol design allows for a variable number of hash functions (k). However, Squid employs a very efficient method using a fixed number - four. {\bf Rather than computing a number of independent hash functions over a URL Squid uses a 128-bit MD5 hash of the key (actually a combination of the URL and the HTTP retrieval method) and then splits this into four equal chunks. Each chunk, modulo the digest size (m), is used as the value for one of the hash functions - i.e. an index into the bit array.}  Note: As Squid retrieves objects and stores them in its cache on disk, it adds them to the in-RAM index using a lookup key which is an MD5 hash - the very one discussed above. This means that the values for the Cache Digest hash functions are already available and consequently the operations are extremely efficient!''  (``Key'' here just means hash input, as in ``key-value pair''.)}
\item Not sure what Bloom filter-like data structures would have randomized querying procedures (``unsteady representations'').  They mention the possibility of differential privacy mechanisms being incorporated into the querying procedure.  But what's the purpose of this, if the security definition gives the adversary the set~$S$?  (What are you keeping private?) 
\end{itemize}
